---
title: "Reproducibility Report: Group A Choice 3"
output:
  html_document:
    toc: yes
    toc_float: yes
  pdf_document:
    toc: yes
---

-------

For this exercise, please try to reproduce the results from Experiment 6 of the associated paper (Shah, Shafir, & Mullainathan, 2015). The PDF of the paper is included in the same folder as this Rmd file. 

#### Methods summary:

The authors were interested in the effect of scarcity on people's consistency of valuation judgments. In this study, participants played a game of Family Feud and were given either 75 s (budget - "poor" condition) or 250 s (budget - "rich" condition) to complete the game. After playing the game, participants were either primed to think about a small account of time necessary to play one round of the game (account -"small" condition) or a large account (their overall time budget to play the entire game, account - "large" condition.) Participants rated how costly it would feel to lose 10s of time to play the game. The researchers were primarily interested in an interaction between the between-subjects factors of scarcity and account, hypothesizing that those in the budget - "poor" condition would be more consistent in their valuation of the 10s regardless of account in comparison with those in the budget - "rich" condition. The authors tested this hypothesis with a 2x2 between-subjects ANOVA.

------

#### Target outcomes: 

Below is the specific result you will attempt to reproduce (quoted directly from the results section of Experiment 6):

> "One participant was excluded because of a computer
malfunction during the game. Time-rich participants
rated the loss as more expensive when they thought
about a small account (M = 8.31, 95% CI = [7.78, 8.84])
than when they thought about a large account (M = 6.50,
95% CI = [5.42, 7.58]), whereas time-poor participants’
evaluations did not differ between the small-account
condition (M = 8.33, 95% CI = [7.14, 9.52]) and the large account
condition (M = 8.83, 95% CI = [7.97, 9.69]). A 2
(scarcity condition) × 2 (account condition) analysis of
variance revealed a significant interaction, F(1, 69) = 5.16,
p < .05, ηp2 = .07." (Shah, Shafir & Mullainathan, 2015)
------

```{r global_options, include=FALSE}
knitr::opts_chunk$set(echo=TRUE, warning=FALSE, message=FALSE)
```

## Step 1: Load packages

```{r}
library(tidyverse) # for data munging
library(knitr) # for kable table formating
```


```{r}
library(haven) # import and export 'SinsPSS', 'Stata' and 'SAS' Files
library(readxl) # import excel files

# #optional packages:
# library(afex) #anova functions
# library(langcog) #95 percent confidence intervals
```

# Step 2: Load data

```{r}
# Just Experiment 6
data <- read_excel("data/study 6-accessible-feud.xlsx")
```

# Step 3: Tidy data

The data are already tidy as provided by the authors.

# Step 4: Run analysis

## Pre-processing

> One participant was excluded because of a computer malfunction during the game (Shah, Shafir, & Mullainathan, 2015, p. 408)

Note: The original paper does not identify the participant that was excluded, but it was later revealed through communication with the authors that it was participant #16. The exclusion is performed below. 

```{r}
# Participant #16 should be dropped from analysis 
excluded <- "16"

d <- data %>%
  filter(!Subject %in% excluded) #participant exclusions
```

## Descriptive statistics

> Time-rich participants rated the loss as more expensive when they thought about a small account (M = 8.31, 95% CI = [7.78, 8.84]) than when they thought about a large account (M = 6.50, 95% CI = [5.42, 7.58]), whereas time-poor participants’ evaluations did not differ between the small-account condition (M = 8.33, 95% CI = [7.14, 9.52]) and the large- account condition (M = 8.83, 95% CI = [7.97, 9.69]). (Shah, Shafir, & Mullainathan, 2015, p. 408)

```{r}
# reproduce the above results here

# group by condition 
by_cond <- d %>% group_by(Cond)
```


```{r}

# determine the means of the grouped data and other valus for calculating the confidence intervls. can also guess the conditions based on the means   
stats <- summarise( by_cond,
  mean = mean(expense),
  sd = sd(expense),
  n = length(expense),
  se = sd/ sqrt(n)

)
```

```{r}
#  guess z-score that corresponds to confidence interval, then calculate confidence intervals for each group 
alpha = 0.001
z_score = 1.96
stats %>% summarise(
  margin_error = z_score * se,
  lower_bound = mean - margin_error,
  mean2 = mean,
  upper_bound = mean + margin_error
)


# reference: https://www.statisticshowto.com/probability-and-statistics/confidence-interval/#CIZ2
```


## Inferential statistics

> A 2 (scarcity condition) × 2 (account condition) analysis of variance revealed a significant interaction, F(1, 69) = 5.16, p < .05, ηp2 = .07.

```{r}

# two way anova to study interaction between the conditions... => data only has levels 0 - 3 in a single column, which need to be grouped...
# scarcity conditions are time rich: [1,3] vs time poor [0,2]
# account conditions are small account [1, 0] vs big account [3,2]

# create a new column time_rich, where if Cond = 1,3, time_rich =1. Otherwise, = 0. Same for big_account

new_data <- data %>%
  mutate(time_rich = case_when(
    data$Cond %in% c(1,3) ~ 1,
    data$Cond %in% c(0,2) ~ 0
    )) %>%
    mutate(big_account = case_when(
    data$Cond %in% c(3,2) ~ 1,
    data$Cond %in% c(1,0) ~ 0
    ))
```


```{r}
# now can do interaction test 

interaction <- aov(expense ~ time_rich * big_account, data = new_data)
summary(interaction)

# ref: https://www.scribbr.com/statistics/two-way-anova/
```
```{r}
library(lsr)
```


```{r}
etaSquared(interaction)

# ref: https://www.r-bloggers.com/2022/01/how-to-perform-eta-squared-in-r/
```

# Step 5: Reflection

Were you able to reproduce the results you attempted to reproduce? If not, what part(s) were you unable to reproduce?

> I was mostly able to reproduce the results I attempted. I got the same mean and confidence intervals in the descriptive statistics section. I also showed that the interaction between variables in the inferential statistics section was significant with p < .05, and demonstrated a partial eta squared of 0.07. However, I did not get the same F-score.

How difficult was it to reproduce your results? 

> It was quite difficult.

What aspects made it difficult? What aspects made it easy?

> It was difficult because I am not extremely familiar with the statistical tests the authors used, and there seem to be many ways on the internet to calculate confidence intervals and interaction. Also, the authors did not use very descriptive naming for their variables, which means I had to infer which condition was which. The task was made easier by the ability to use the internet.
